\documentclass[english]{short-notes}

\usepackage{math-ag}

\addbibresource{global.bib}
%\bibliography{global.bib}

\title{Perverse Sheaves}
\author{Clemens Koppensteiner}

\begin{document}

\newcommand*\muperv{\perv[μ]}
\renewcommand*\SS{\operatorname{SS}}

\maketitle

\tableofcontents

\section{Constructible sheaves}

Let $X$ be a real analytic manifold.

\remark{\cite[Definition 8.2.1]{KashiwaraSchapira:1994:SheavesOnManifolds}}%
Let $Z$ be a subset of $X$. One says that $Z$ is subanalytic at $x ∈ X$ if there exists an open neighborhood $U$ of $x$, compact manifolds $Y^i_j$ ($i =1,2$, $1 \le j \le N$) and morphisms $f^i_j\colon Y^i_j$ such that
\[
Z \cap U = U \cap \bigcup_{j=1}^N \left( f¹_j(Y¹_j) \setminus f²_j(Y²_j) \right).
\]
If $Z$ is subanalytic at each $x ∈ X$, one says that $Z$ is subanalytic in $X$.

\begin{Def}
    \remark{\cite[Definition 8.4.3]{KashiwaraSchapira:1994:SheavesOnManifolds}}%
    An object $\sheaf F$ of $D^b(X)$ is called weakly $ℝ$-constructible, if there exists a locally finite covering $X = \bigcup X_i$ by subanalytic subsets such that for all $j ∈ ℤ$ and all $i$ the sheaves $\res{H^j(F)}{X_i}$ are locally constant.
\end{Def}


\section{Microlocal description}

Let $X$ be a real analytic manifold.

\begin{Def}
    \remark{\cite[Definition 5.1.2]{KashiwaraSchapira:1994:SheavesOnManifolds}}%
    Let $\sheaf F ∈ D^b(X)$.
    Then \emph{micro-support} of $\sheaf F$, denoted by $\SS(\sheaf F)$, is the subset of points $p ∈ T^*X$ for which the following condition does \emph{not} hold:

    There exists an open neighborhood $U$ of $p$ such that for each $x ∈ X$ and every real continuous function $ψ$ defined in a neighborhood of $x$, with $ψ(x) = 0$, $dψ(x) ∈ U$, we have
    \[
    (RΓ_{\{x : ψ(x) \ge 0\}} (\sheaf F))_{x} = 0.
    \]
\end{Def}

\begin{Lem}
    The intersection of $\SS(\sheaf F)$ with the zero section of $T^*X$ is $\supp(\sheaf F)$.
\end{Lem}

\begin{Prop}
    \remark{\cite[Theorem 8.4.2]{KashiwaraSchapira:1994:SheavesOnManifolds}}%
    Let $\sheaf F ∈ D^b(X)$.
    The following are equivalent:
    \begin{enumerate}
        \item $\sheaf F$ is weakly $ℝ$-constructible.
        \item $\SS(\sheaf F)$ is contained in a closed conic subanalytic isotropic subset.
        \item $\SS(\sheaf F)$ is a closed conic subanalytic Lagrangian subset.
    \end{enumerate}
\end{Prop}
Let $X$ be a complex manifold.

\begin{Def}
    \remark{\cite[Definition 7.5.4]{KashiwaraSchapira:1994:SheavesOnManifolds}}%
    Let $Λ$ be a Lagrangian submanifold of $T^*X$, $p ∈ Λ$ and let $\sheaf F ∈ D^b(X)$.
    Assume that $\SS(\sheaf F) \subseteq Λ$ in a neighborhood of $p$ and let $φ$ be a function transversal to $Λ$ at $p$.
    Let $d$ be a number satisfying 
    \[
    d \equiv \frac12 \dim (λ_\circ(p) \cap λ_Λ(p)) \bmod ℤ.
    \]
    Let $τ_φ(p) = τ(λ_\circ(p), λ_Λ(p), λ_φ(p))$, and let $L ∈ D^b(\catModules A))$.
    If there is an isomorphism
    \[
    RΓ_{\{φ\ge 0\}}(\sheaf F)_{π(p)}[-d + \frac12 \dim X + \frac 12 τ_φ(p)] \cong L,
    \]
    then one says $\sheaf F$ is of type $L$ with shift $d$ at $p$.
\end{Def}

\begin{Def}
    \remark{\cite[Definition 10.3.7]{KashiwaraSchapira:1994:SheavesOnManifolds}}%
    Denote by $\muperv D^{\le n}_{w-ℂ-c}(X)$ (resp.~$\muperv D^{\ge n}_{w-ℂ-c}(X)$) the full subcategory of $D^b_{w-ℝ-c}(X)$ (the subcategory of $D^b(X)$ consisting of objects with weakly $ℝ$-constructible cohomology) consisting of objects $\sheaf F$ such that the type $L$ of $\sheaf F$ with shift $0$ at any non-singular point of $\mathrm{SS}(\sheaf F)$ satisfies $H^j(L) = 0$ for $j > n-\dim X$ (resp. $j < n - \dim X$).
\end{Def}

\printbibliography

\end{document}
